---
title:  "6060 Practice Quiz 3"
author: "Veesta Mavandadi"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
    
---
# Hypotheses

For simple linear regression, the chief null hypothesis is H0 : β1 = 0, and the corresponding alternative hypothesis is H1 : β1 6= 0. If this null hypothesis is true, then, from E(Y ) = β0 + β1x we can see that the population mean of Y is β0 for every x value, which tells us that x has no effect on Y . The alternative is that changes in x are associated with changes in Y. 

#Analysis Plan for Each Hypothesis 

A statistical power analysis was performed for sample size estimation, based on data from pilot study/published study X (N=…), comparing …. to ….. The effect size (ES) in this study was …., considered to be extremely large/large/medium/small using Cohen's (1988) criteria. With an alpha = .05 and power = 0.80, the projected sample size needed with this effect size (GPower 3.1 or other software) is approximately N = ….. for this simplest between/within group comparison. Thus, our proposed sample size of ..N+.. will be more than adequate for the main objective of this study and should also allow for expected attrition and our additional objectives of controlling for possible mediating/moderating factors/subgroup analysis, etc.


A simple linear regression was calculated to predict DV based on IV. Examine by how many units does the DV change for each unit increase of the IV. 

The associations between dependent and independent variables are presented by means of unstandardized linear regression coefficients and 95% confidence intervals. 


#Results with APA Style Table - apa.reg.table

Descriptive Statistics: Mean (SD) of IV and DV. Range of values 

As planned, we used a linear regression analysis to predict DV from IV (b = .#, 95% CI[#,#]). The CI is fairly ___, but indicates that each unit of additional IV is associated with a # unit of additional DV (# to # scales). Relative to other predictors of DV, this is a ___ relationship. One caution in this analysis is the (outliers;restricted range;out of range estimates; predicting for something not in the data set; not a random sampling).

Make specific predictions: 
CI FOR MEAN: Based on this regression analysis, participants with a IV score of # would be predicted to have a DV of #, 95% CI[#,#]. This indicates that the DV in this group is likely to be (meaningful descriptor of DV). 

PI FOR INDIV VALUE: Based on this regression analysis, a participant with a IV score of # would be predicted to have a DV of #, 95% PI[#,#]. This is a /very long/ prediction interval, but it indicates that a participant at this /low/ score on the IV is very /unlikely/ to be a the /highest/ level for DV. 

A significant regression equation was found (F(#,#)=#,p=#), with an R2 of #. 


```{r,echo=FALSE,message=FALSE, warning=FALSE}
# Code goes in blocks like this

# load libraries
library(tidyverse)
library(cocor)

```

#Relations among variables 

## Scatter plot for Negative Affect and Neuroticism 

Below you can see the correlation between negative affect and neuroticism with a regression line. 

```{r,echo=FALSE,message=FALSE, warning=FALSE}

## Create NA-Neur Scatter Plot
my.scatter <- qplot(x=neg_affect,y=Neuroticism,data=analytic_data_female)

#add a regression line, without the confidence interval se = false 
#correlations in r page 6 

my.scatter <- my.scatter + geom_smooth(method = "lm", se = FALSE, color='black')

my.scatter <- my.scatter + labs(x="Negative Affect",y="Neuroticism")
my.scatter <- my.scatter + theme_classic()
my.scatter <- my.scatter + theme(axis.line.x = element_line(colour = 'black',size=0.5, linetype='solid'),
                                 axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

print(my.scatter)
```
